Letter from ANU

### 2025-07-29 cover_letter/letter.qmd
Include a statement in cover letter stating that we want to do single-anonymous

>>>>

We understand that the Journal of Computational and Graphical Statistics now uses a single-anonymous peer review system by default, with an option for authors to opt into double-anonymous review. We intend to proceed with the single-anonymous review, and thus our manuscript includes full author information. Since the submission system requires uploading two PDF files, one with author details and one anonymized, please note that the anonymized version is identical to the version containing author information.
